{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Simulation results, Appliaction

%	\section{Colour Guide}
%		\begin{itemize}
%			\item {\color{red} RED}: is for general comments for your own text
%			\item {\color{green} GREEN}: is for Jona's comments
%			\item {\color{orange} ORANGE}: is for Jonghun's comments
%			\item {\color{blue} BLUE}: is for Jakob's comments
%		\end{itemize}

@@

	Functional Data Analysis (FDA), which has its roots in the work of Ulf Grenander and Kari Karhunen, is gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, FDA has advantages in that it allows extracting information given by properties such as the smoothness of the underlying process or its derivatives (cf. \cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves or functions.	 
	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions. Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples, an example which will be used in later parts of this paper.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}  
	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as described by Equation \ref{DGP1}.

	 \begin{equation}\label{DGP1}
	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
	 	\qquad i = 1, ..., N
	 \end{equation}

	Here, $X(\omega)$ is a random function, $Y(\omega)$ is a scalar response variable and $\beta(t)$ is a coefficient function. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional. This paper then introduces two distinct ways of estimating $\beta(t)$ using approximations dependent on a parameter choice and explores the selection of these parameters using cross validation.\\

	In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe two methods of estimating a scalar coefficient function using using the concepts of basis expansion and functional principal component analysis. Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis and truncation parameter for the aforementioned methods. The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves. In Section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.

@@

	\subsection{Inner Products and Hilbert Spaces}
	In the following we restrict our analysis to vector spaces over $\mathbb{R}$ but more a general formalization including other fields is possible. Let $\mathbb{V}$ be a vector space over $\mathbb{R}$.  Then, a function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{R}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.

@@

	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion around a chosen point can often lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole. From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$. As in the case of the Taylor expansion, it is not necessary to approximate a function around zero as shown above, instead one can introduce a shift parameter. This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.

@@

	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi i x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
	\end{equation}

@@

	%{\color{blue}I don't get this... Isn't the basis defined independently from the data set? Why is this dependent on the measuring points? "rephrasing \cite{ramsay_functional_2005}, the Fourier basis is orthonormal when the values $t_j$ are equally spaced within $T$."}

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree. Typically, knots are placed on an equidistant grid leading to polynomials on neighboring subintervals matching derivatives up to order $m-2$ at the boundary knot $\tau_l$. However, in some settings it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure. This allows for a reduced number of matching derivatives at the corresponding knots. For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\

	B-splines were developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure. Let $\phi_{l,m}^{BS}(x) \quad l \in \{1,\dots,L-1\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and inner knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.

@@

	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times. This padding of the knot vector then allows to calculate every object that is needed for the definition of the chosen basis.\\

@@

@@

	\begin{figure}[H]
		\includegraphics[width=\textwidth]{../Graphics/basis_expansions.pdf}
		\caption{B-spline Approximations of NIR Absorption Spectra with different Basis Truncation Parameters}
	\end{figure}

@@

	where the $c(t,s)$ are \textit{Hilbert-Schmidt Kernels} defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be a \textit{Hilberst-Shmidt operator} on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by

@@

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{N}\sum_{i = 1}^{N}x_i(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{N} \sum_{i = 1}^{N} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
	\end{equation}

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m = 1, \dots, N-1\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation. As in the case of ordinary principal components, the number of eigenfunctions corresponding to non-zero eigenvalues is limited (cf. chapter 8.2.3 \cite{ramsay_functional_2005}). As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality. However the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as

@@

	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of both the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.

@@

	This method of deriving or approximating the eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda. The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method.

@@

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{Z}_{N,1} & \dots & \tilde{Z}_{N,J}
		\end{pmatrix}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{N-1} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}\label{fpcr_reg_both_expansions}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m = 1}^{N-1} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i & = \tilde{\alpha}^L
			+ \sum_{m = 1}^{N-1} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right] 
			+ \epsilon_i \\
			& = \tilde{\alpha}^L
			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m = 1}^{N-1} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
			+ \epsilon_i \\
			& \approx \tilde{\alpha}^L
			+ \sum_{m = 1}^{N-1} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{\xi}^{1,L}_{N} & \dots & \tilde{\xi}^{M,L}_{N}
		\end{pmatrix}
	\end{equation}

@@

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a generated B-spline basis which is created using 50 knots. These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drawn from a multivariate normal distribution $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$. Finally, we obtain the generated curves $NIR_{sim}$

	{\color{blue} This has to be more precise. We don't really use $\hat{\nu}_j(t)$ but $\tilde{\nu}^{m,L}(t)$ for a large $L$.}

	\begin{equation}
		\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)
	\end{equation}

	where $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.

@@

	\subsection{Results}

	\subsubsection{Basis Expansion Regression}
	The following results origin from the \hyperref[basis_exp_transf]{\textbf{Estimation using Basis-Representation}}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.

	\paragraph{Monomial Basis}
	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis. For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than B-splines for this coefficient function, but show the weakest performance for the coefficient function $f_2$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less pronounced.

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happened here exactly?}
	The smooth function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$. For $f_2$, 11(6) B-spline basis functions are needed for the high(low) signal-to-noise ratios. For $f_2$, the B-spline basis functions outperform the monomial basis but come second to the Fourier basis.

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for the bumpy function $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio. With the low signal-to-noise ratio, the simulation chooses a smaller number to account for the higher noise in the response variable. The Fourier basis functions perform the best in each setup for the basis expansion regression. When recalling $f_1$ and $f_2$, both, but especially $f_1$ shows similar curvature order across the domain which contributes to the strong performance of this basis.	\\

>>>>

	\section{Colour Guide}
		\begin{itemize}
			\item {\color{red} RED}: is for general comments for your own text
			\item {\color{green} GREEN}: is for Jona's comments
			\item {\color{orange} ORANGE}: is for Jonghun's comments
			\item {\color{blue} BLUE}: is for Jakob's comments
		\end{itemize}

@@

	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	As \cite{kokoszka_introduction_2017} {\color{red}(page ca. 17)} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves .

	In functional data analysis, the concept of a data set includes both realizations of scalar random variables and realizations of random functions. These could be the absorption of the Near-infrared (NIR) spectrum, which will be used in later parts of this paper. NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of light at different wavelengths in a sample. \footnote{For more details, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}  This dataset can then be used, for example, to predict a scalar response variable. To conduct functional linear regression, we need to consider several new concepts and methods that distinguish it from multivariate linear regression.
	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as described by Equation \ref{DGP1}.

	 \begin{equation}\label{DGP1}
	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
	 	\qquad i = 1, ..., n
	 \end{equation}

	 Here, $X(\omega)$ is a random function, $Y(\omega)$ is the response variable and $\beta(s)$ the coefficient function. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional. As in the framework of scalar linear regression, estimating $\beta(t)$ is particularly interesting for prediction or inference. \\

	 In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe two methods of estimating a scalar coefficient function using using the concepts of basis expansion and functional principal component analysis. Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis for the previously mentioned methods. The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves. In section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.

@@

	\subsection{Inner Products and Hilbert Spaces}
	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$. A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.

@@

	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion can often lead to reasonable approximations around a specific point or even on $\mathbb{R}$ as a whole. From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$. As in the case of the Taylor expansion, it is not necessary to approximate a function around zero as shown above, instead one can introduce a shift parameter. This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.

@@

	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi n x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_n \cos(2\pi n x) + b_n \sin(2\pi n x)\right]
	\end{equation}

@@

	{\color{blue}I don't get this... Isn't the basis defined independently from the data set? Why is this dependent on the measuring points? "rephrasing \cite{ramsay_functional_2005}, the Fourier basis is orthonormal when the values $t_j$ are equally spaced within $T$."}

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree. Typically, knots are placed on an equidistant grid, but deviations from this principle can prove advantageous in atypical settings. Additionally, at each $\tau_l$, the polynomials on neighboring subintervals must match derivatives up to order $m-2$ at the boundary. However, it is sensible to place multiple knots at the same value to replicate specific properties of the data structure. A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}. Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.

@@

@@

	{\color{red}Explain what happens when $l+m+1 > L$ !!!(I don't get it)\\
		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.(adressed)}

@@

@@

	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by

@@

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{n}\sum_{i = 1}^{n}x_i(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{n} \sum_{i = 1}^{n} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
	\end{equation}

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m \in \mathcal{M}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ as the solutions of the following equation. {\color{red} I think the number of principal components has to be smaller then the number of observations. So I can give more information about $\mathcal{M}$.}

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as

@@

	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the curves for both the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.

@@

@@

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
		\end{pmatrix}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathcal{M}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \hat{\mu}(s) + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \hat{\nu}^m(s) \phi_j(s) \right] \right] \mathrm{d}s + \epsilon_i \\
			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j \in \mathcal{I}} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}\label{fpcr_reg_both_expansions}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			y_i & = \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right] 
			+ \epsilon_i \\
			& = \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
			+ \epsilon_i \\
			& \approx \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

@@

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{\xi}^{1,L}_{n} & \dots & \tilde{\xi}^{M,L}_{n}
		\end{pmatrix}
	\end{equation}

@@

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset, motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a generated cubic B-spline basis which is created using 50 knots. In the R implementation of the fda package that is used, these 50 knots account for 52 basis functions (50+4-2). These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. It is assumed that the scores follow a normal distribution, so the new realizations for the scores are drawn from a multivariate normal distribution $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{M}\right)' \sim \mathcal{N}(0_M, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_M))$. Finally, we obtain the generated curves $NIR_{sim}$

	\begin{equation}
		\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{m = 1}^{M} \tilde{\xi}_m(\omega) \tilde{\nu}^{m,L}(t)
	\end{equation}

	where $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\tilde{\nu}^{m,L}(t)$  are approximated as vectors in $\mathbb{R}^{401}$ for $L =$ 30 eigenfunctions.

@@

	\subsection{Results}	
	The discussed results and figures of $\hat{\beta}$ for the simulation can be found in the appendix. 
	\subsubsection{Basis Expansion Regression}
	The following results origin from the \hyperref[basis_exp_transf]{\textbf{Estimation using Basis-Representation}}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, which is then tractable with typical multivariate regression theory.

	\paragraph{Monomial Basis}
	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability. For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$. The monomial basis shows a better performance than B-splines for this coefficient function. A hypothesis for this could be that $f_1$ resembles an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, which is visible in figure 9 and 10, where it seems like $\hat{\beta}$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2,Y_2$ this weakness is still visible, but less pronounced.

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happened here exactly?}
	The smooth function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$. An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (figure 7 and 8), which is especially pronounced for the higher noise responses. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratios. For $f_2$, the B-spline basis functions outperform the monomial basis but come second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ (figure 9 and 10).
